### 2021-06-10 paper/appendix_data.tex
Add new results.
Fix latex errors.
Update the section on the number of contacts.

Thus, we can use the empirical distributions from this data as pre-pandemic number of
contacts.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9 \textwidth]{../figures/assortative_matching_probability_example}
    \caption{Distribution of random non-work contacts by age of participants.}
    \label{fig:assortativity}
    \figurenotes{The figure shows the distribution of random non-work contacts by age
        groups. A row shows the share of contacts a certain age group has with all other
        age groups. Higher values are colored in darker red tones. The diagonal
        represents the share of contacts with individuals from the same age group.}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/rapid_test_demand_shares}
    \caption{\textbf{Share of Individuals that do a Rapid Test.} \comment[id=J]{Talk
        about the interpretation of each line.}}
    \label{fig:rapid_test_demand}
\end{figure}

>>>>

Simplifying the number of contacts, we arrive at the following distributions of the
numbers of contacts by contact type.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/other_non_recurrent}
    \caption{Number of Non Recurrent Other Contacts}
    \label{n_contacts_other_non_recurrent}
    \floatfoot{\noindent In the model it is sampled every day which of these numbers of
    contacts a person is planned to have. Note that the contact diaries include such high
    values that super spreading events are well possible in our model. The planned number
    of contacts is reduced by policies, seasonality and individual responses to events
    such as receiving a positive rapid test to the number of actual contacts with
    transmission potential. Other contacts include all contacts that are not household
    members, school contacts or work contacts, for example leisure contacts or contacts
    during grocery shopping.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/other_recurrent_daily}
    \caption{Number of Daily Recurrent Other Contacts}
    \label{n_contacts_other_daily_recurrent}
    \floatfoot{\noindent Individuals are assigned to groups that are time constant and
    that meet daily. The share of individuals that attend in a way that has transmission
    potential is reduced by policies, seasonality and individual responses to events such
    as receiving a positive rapid test. Other contacts include all contacts that are not
    household members, school contacts or work contacts, for example leisure contacts or
    contacts during grocery shopping.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/other_recurrent_weekly}
    \caption{Number of Weekly Recurrent Other Contacts}
    \label{n_contacts_other_weekly_recurrent}
    \floatfoot{\noindent Individuals are assigned to up to four groups that are time
    constant and that meet weekly. The share of individuals that attend in a way that has
    transmission potential is reduced by policies, seasonality and individual responses
    to events such as receiving a positive rapid test. Other contacts include all
    contacts that are not household members, school contacts or work contacts, for
    example leisure contacts or contacts during grocery shopping.}
\end{figure}

% work contacts

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/work_non_recurrent}
    \caption{Number of Non Recurrent Work Contacts}
    \label{n_contacts_work_non_recurrent}
    \floatfoot{\noindent In the model it is sampled every day which of these numbers of
    contacts a working person is planned to have. Note that the contact diaries include
    such high values that super spreading events are well possible in our model. The
    planned number of contacts is reduced by policies, seasonality and individual
    responses to events such as receiving a positive rapid test to the number of actual
    contacts with transmission potential. Work contacts only take place between working
    individuals.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/work_recurrent_daily}
    \caption{Number of Daily Recurrent Work Contacts}
    \label{n_contacts_work_daily_recurrent}
    \floatfoot{\noindent Working individuals are assigned to groups that are time
    constant and that meet daily to match the given distribution of daily work contacts.
    You can think of these as for example colleagues with which one shares an office
    space. The share of individuals that attend in a way that has transmission potential
    is reduced by policies (such as a work from home mandate), seasonality and individual
    responses to events such as receiving a positive rapid test. Work contacts only take
    place between working individuals.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/work_recurrent_weekly}
    \caption{Number of Weekly Recurrent Work Contacts}
    \label{n_contacts_work_weekly_recurrent}
    \floatfoot{\noindent Working individuals are assigned to up to 14 groups that are time
    constant and meet weekly. Groups are scheduled to meet on separate days of the work
    week. These contact models cover weekly team meetings etc. The share of individuals
    that attend in a way that has transmission potential is reduced by policies,
    seasonality and individual responses to events such as receiving a positive rapid
    test. Work contacts only take place between working individuals.}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/data/assortativity_other_non_recurrent}
    \caption{Distribution of Random Other Contacts by Age Group}
    \label{fig:assortativity}
    \figurenotes{The figure shows the distribution of random non-work contacts by age
        groups. A row shows the share of contacts a certain age group has with all other
        age groups. Higher values are colored in darker red tones. The diagonal
        represents the share of contacts with individuals from the same age group.}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/rapid_test_demand_shares}
    \caption{\textbf{Share of Individuals that do a Rapid Test.}}
    \figurenotes{\textcolor{red}{J: Talk about the interpretation of each line.}}
    \label{fig:rapid_test_demand}
\end{figure}
